### 2021-02-20 paper.tex
Add tab screenshot.

UC2 / UC5
The visualization of the information related to a specific class (UC2) / instance (UC5).
The adjacent nodes of any specific resource (class or instance) can be visualized with the star operators (see section \enquote{Star}).
A view of a specific resource with details such as definition, chapter, alternative labels and textbook page numbers is presented using an installation of the LodView RDF browser~\cite{lodview} with a modified color scheme according to the SNIK subontology color coding.

@@

\subsection*{Tabs}
%For this subgraphs of the ontology have to be extracted and organized.
%A feature of SNIK Graph, tabs, allows multi-instance usage.
%One major issue in working with SNIK Graph was the missing ability of organizing teaching scenarios.
To organize teaching scenarios, independent SNIK Graph instances are loaded into containers\footnotemark{} that can be organized around the browser window.
\footnotetext{Implemented using the JavaScript GoldenLayout framework (\url{https://golden-layout.com/}).} 
These containers can either be accessed as tabs or freely partitioned.

%This feature allows better workflows in preparation and presentation of teaching scenarios.
%Additionally the design allows to store and restore sessions, that can be shared around computers and persons.
%We use JSON formatted files for export and import.

\subsection*{Compound Layout}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{combine.pdf}
    \caption{Grouping of equivalent concepts from different sources in SNIK Graph (color coded).}% using the \enquote{combine matches} option.}
	\label{fig:combine}
\end{figure}
\vspace{-3pt}
%\noindent For citations of references, we prefer the use of square brackets and consecutive numbers, e.g. as shown by Author et al. [2], [3, pp. 5–10], as mentioned earlier [1], [3], [9]. The following bibliography provides the basic formats as a reference list with entries for journal articles [1], book chapter [2], as well as a URL [5]. For further guidance please refer to the \href{https://ieeeauthorcenter.ieee.org/wp-content/uploads/IEEE-Reference-Guide.pdf}{IEEE-Reference-Guide}.

>>>>

UC2 / UC5
The visualization of the information related to a specific class (UC2) / instance (UC5).
The adjacent nodes of any specific resource (class or instance) can be visualized with the star operators (see section \enquote{Star}).
A view of a specific resource with details such as definition, chapter, alternative labels and textbook page numbers is presented using an installation of the LodView RDF browser~\footnote{\url{https://lodview.it/}} with a modified color scheme according to the SNIK subontology color coding.

@@

\subsection*{Tabs and Containers}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{tabs.png}
    \caption{A session containing the default view and freely partitioned subgraphs containers.}
	\label{fig:tabs}
\end{figure}
\vspace{-3pt}
%For this subgraphs of the ontology have to be extracted and organized.
%A feature of SNIK Graph, tabs, allows multi-instance usage.
%One major issue in working with SNIK Graph was the missing ability of organizing teaching scenarios.
To organize teaching scenarios, independent SNIK Graph instances are loaded into containers\footnotemark{} that can be organized around the browser window.
\footnotetext{Implemented using the JavaScript GoldenLayout framework (\url{https://golden-layout.com/}).} 
These containers can either be accessed as tabs or freely partitioned see \cref{fig:tabs}.
The content and of the all containers can be saved and loaded as a session to continue developing a teaching scenario at a later point.

%This feature allows better workflows in preparation and presentation of teaching scenarios.
%We use JSON formatted files for export and import.

\subsection*{Compound Layout}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{combine.pdf}
    \caption{Grouping of equivalent concepts from different sources in SNIK Graph (color coded).}% using the \enquote{combine matches} option.}
	\label{fig:combine}
\end{figure}
\vspace{-3pt}
%\noindent For citations of references, we prefer the use of square brackets and consecutive numbers, e.g. as shown by Author et al. [2], [3, pp. 5–10], as mentioned earlier [1], [3], [9]. The following bibliography provides the basic formats as a reference list with entries for journal articles [1], book chapter [2], as well as a URL [5]. For further guidance please refer to the \href{https://ieeeauthorcenter.ieee.org/wp-content/uploads/IEEE-Reference-Guide.pdf}{IEEE-Reference-Guide}.
